The hydra and the rooster

### 2020-07-18 latex/chapter-ordinals.tex
simplification of class OrdinalNotation

Our definition of ordinal notation is inspired by our use of \coq{}: defining inductive data types, predicates, functions, etc, and proving properties of these functions. 
The following type class describes a well-ordered type, and specifies functions for comparing two ordinals, and checking wether a given  ordinal is $0$, a limit or a successor.

@@

\begin{Coqsrc}
Class OrdinalNotation {A:Type}{lt: relation A}(sto:StrictOrder lt)
      (compare : A -> A -> comparison)  :=
  {   wf : well_founded lt;
      compare_correct :
         forall alpha beta:A,
          CompareSpec (alpha=beta) (lt alpha beta) (lt beta alpha)
                                   (compare alpha beta);
      ZeroLimitSucc_dec : forall alpha,
        {Least alpha} +
        {Limit alpha} +
        {beta: A | Successor alpha beta}
  }. 
\end{Coqsrc}

@@

>>>>

Our definition of ordinal notation is inspired by our use of \coq{}: defining inductive data types, predicates, functions, etc, and proving properties of these functions.

@@

\begin{Coqsrc}
Class OrdinalNotation {A:Type}{lt: relation A}(sto:StrictOrder lt)
      (compare : A -> A -> comparison)  :=
  {   wf : well_founded lt;
      compare_correct :
         forall alpha beta:A,
          CompareSpec (alpha=beta) (lt alpha beta) (lt beta alpha)
                                   (compare alpha beta);
  }. 
\end{Coqsrc}

@@

\begin{todo}
Present the method ZeroLimitSucc 
\end{todo}
